---
title: "HW1"
date: today
author: Fa-Hsiang Yin
format:
 pdf:
    include-in-header:
      - text: |
         \usepackage{setspace,relsize}
mainfont: "Microsoft JhengHei UI"
toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
```

```{r}
library(palmerpenguins)
library(dplyr)
library(ggplot2)
library(Hmisc)
theme_set(theme_minimal())
```

# Summary Staistic

```{r}
#| output: asis

latex(describe(penguins_raw), file = "", caption.placement = "top")
```

# Missing Values

```{r}
#| output: asis
library(Hmisc)
library(DataExplorer)
plot_missing(penguins_raw)
```

Note that the variable "Comment" is additional information for certain situations causing the missing values, we can just ignore it.

We also notice that missing values can be roughly categorized into three situations as follows:

1.  Missing body measurements : includes culmen length, culmen depth, flipper length and body mass.

2.  Missing blood isotope measurement : missing delta 15 N or both delta 15 N and delta 13 C.

3.  Missing gender info.

When situation 1 occurs, situation 2 and 3 will also occur. (Comment: Adult not sampled.)

```{r}
mypenguins <- penguins_raw[,-17]
```

# Male v.s.Female: Body Measurement

## Table1

```{r}
library(tidyverse)
library(table1)
pen_table<- mypenguins%>%
            drop_na(Sex)%>%
  `names<-`(replace(names(.),1:16,gsub(" ", "_",names(.),
            fixed = TRUE)))%>%
  `names<-`(replace(names(.),c(10,11,12,13,15,16),
            c('Culmen_Length','Culmen_Depth',
              'Flipper_Length','Body_Mass',
              'Delta_15_N','Delta_13_C')))
table1(~ Culmen_Length+Culmen_Depth+Flipper_Length+Body_Mass+Delta_15_N+Delta_13_C|Sex,pen_table)
```

## Graph

```{r}
library(ggplot2)
library(gridExtra)
library(gapminder)
library(dplyr)
p1 <- ggplot(pen_table,aes(x = Sex,
                           y = Culmen_Length,fill = Sex)) +
      geom_boxplot() +
      scale_y_continuous(name = "Culmen Length(mm)") +
      scale_x_discrete( name = "Sex")
p2 <- ggplot(pen_table,aes(x = Sex,
                           y = Culmen_Depth,fill = Sex)) +
      geom_boxplot() +
      scale_y_continuous(name = "Culmen Depth(mm)") +
      scale_x_discrete( name = "Sex")
p3 <- ggplot(pen_table,aes(x = Sex,
                           y = Flipper_Length,fill = Sex)) +
      geom_boxplot() +
      scale_y_continuous(name = "Flipper Length(mm)") +
      scale_x_discrete( name = "Sex")
p4 <- ggplot(pen_table,aes(x = Sex,
                           y = Body_Mass,fill = Sex)) +
      geom_boxplot() +
      scale_y_continuous(name = "Body Mass(g)") +
      scale_x_discrete( name = "Sex")
p5 <- ggplot(pen_table,aes(x = Sex,
                           y = Delta_15_N,fill = Sex)) +
      geom_boxplot() +
      scale_y_continuous(name = "Isotope:C13") +
      scale_x_discrete( name = "Sex")
p6 <- ggplot(pen_table,aes(x = Sex,
                           y = Delta_13_C,fill = Sex)) +
      geom_boxplot() +
      scale_y_continuous(name = "Isotope:C13") +
      scale_x_discrete( name = "Sex")
grid.arrange(p1,p2,p3,p4,p5,p6,
          ncol = 2, nrow = 3)
```

We can see that the body measurements of male penguins appear to be larger than those of female penguins.

# Species v.s. Island

```{r}
p <- ggplot(data = mypenguins) +
  geom_bar(mapping = aes(x = Island,fill = Species),position = "dodge")
p
```

Of the three species, only the Adelie Penguin (Pygoscelis adeliae) has been observed on all three islands.
